### 2021-04-03 Chapter-3/Chapter-3.tex
update

>>>>

\begin{table*}[]
  \centering\small\footnotesize
  \caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), 
      Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DF),
      The number of instructions\,(\# Instructions), Symbolic Execution\,(SE) and Monte Carlo\,(MC) time.
  }\label{table:over_result}
  \newlength{\x}
  \newlength{\y}
  \settowidth{\x}{~~}
  \settowidth{\y}{m}
  \addtolength{\x}{-1\y}
  \newcommand{\foo}{\mbox{\hspace*{\the\x}}}
  \begin{tabular}{lrrrrrr}
      \hline
      \textbf{Algorithm} & \textbf{Implementation}  & \textbf{\# Leaks} & \textbf{\# CF}         & \textbf{\# DF}
                         & \textbf{\# Instructions}    & \textbf{Time}     \\\hline
                                               &                        &                     &                      &              & ms                     \\\cline{6-6}
      AES &             & 68                     & 0                   & 68                   & 39,855        & 512     \\
      AES &                & 68                     & 0                   & 68                   & 39,855       & 520         \\
      AES &                & 75                     & 0                   & 75                   & 1,704        & 231       \\
      AES &                & 88                     & 0                   & 88                   & 1,350        & 36     \\
      AES&           & 88                     & 0                   & 88                   & 1,350        & 35   \\
      AES &         & 88                     & 0                   & 88                   & 1,420        & 36    \\
      AES &        & 88                     & 0                   & 88                   & 1,586        & 43      \\
      DES &         & 15                     & 0                   & 15                   & 4,596        & 58     \\
      DES &             & 15                     & 0                   & 15                   & 4,596        & 57      \\
      DES &         & 6                      & 0                   & 6                    & 2,976         & 163    \\
      DES &         & 8                      & 0                   & 8                    & 2,593         & 166     \\
      DES &           & 8                      & 0                   & 8                    & 2,593        & 165     \\
      DES &            & 8                      & 0                   & 8                    & 4,260         & 182     \\
      DES &       & 6                      & 0                   & 6                    & 8,272         & 229     \\
                         &    &                    &                     &                      &                  & seconds                  \\\cline{6-6}
      Chacha20 &           & 0                      & 0                   & 0                    & 149,353        & 2         \\  
      Poly1305 &          & 0                      & 0                   & 0                    & 1,213,937      & 15     \\
      Argon2i &          & 0                      & 0                   & 0                    & 4,595,142       & 37    \\
      Ed25519 &           & 0                      & 0                   & 0                    & 5,713,619       & 271     \\
      ECDSA &             & 6                      &    6                & 0                    &  4,214,946     &  48    \\ 
      ECDSA &            &   4                   &   4                 & 0                    &  4,192,558    & 102        \\   
      ECDSA &          &  5                    & 4                   & 1                    &  8,248,322       & 101     \\   
      ECDSA &           &  5                    & 4                   & 1                    &  8,263,599      & 100      \\   
      ECDSA &        &  5                    & 4                   & 1                    &  6,100,465       & 76     \\  
      ECDSA &           & 0                      &  0                   &    0               &  10,244,076       &  121      \\  
      ECDSA &          & 0           &  0                   &  0                 &  9,266,191          & 102    \\

                         &                        &                     &                      &                 & minutes            \\\cline{6-6}
      RSA &           & 6                       & 6                   & 0                    & 22,109,246    & 39      \\
      RSA &            & 12                      & 12                  & 0                    & 24,484,441    & 44        \\
      RSA &           & 107                    & 105                 & 2                    & 17,002,523   & 23  \\
      RSA &           & 38                     & 27                  & 11                   & 14,468,307   & 29    \\
      RSA &           & 36                     & 27                  & 9                    & 15,285,210   & 40      \\
      RSA &          & 31                     & 22                  & 9                    & 16,390,750   & 34      \\
      RSA &         & 4                      &  4                  & 0                    & 18,207,016   & 8         \\
      RSA &            & 8                      &  8                  & 0                    & 18,536,796    & 5       \\
      RSA & & 11& 9& 2& 9,527,231& 2 \\
      RSA & & 14& 14& 0& 10,513,606& 14  \\
      RSA &        & 8                      &  8                  & 0                    & 27,407,986    & 113    \\

      Total              & 904                    & 241                 & 663                & 167,141,947      & 341m  \\\hline
  \end{tabular}
\end{table*}
